A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-08 ASRLab_Thesis_Template/thesis/thesis.tex
Start porting to NCKU template

\documentclass[conference]{IEEEtran}

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{float}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic,algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\graphicspath{{./images/}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading}
% Chinese title: 針對物聯網資料交易的去中心化基礎建設

\author{\IEEEauthorblockN{1\textsuperscript{st} Ching-Hua (Vivian) Lin}
\IEEEauthorblockA{\textit{dept. of CSIE} \\
\textit{National Cheng Kung University}\\
Tainan City, Taiwan (R.O.C.) \\
jkrvivian@gmail.com}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Ching-Chun (Jim) Huang}
\IEEEauthorblockA{\textit{dept. of CSIE} \\
\textit{National Cheng Kung University}\\
Tainan City, Taiwan (R.O.C.) \\
jserv@ccns.ncku.edu.tw}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Chia-Heng Tu}
\IEEEauthorblockA{\textit{dept. of CSIE} \\
\textit{National Cheng Kung University}\\
Tainan City, Taiwan (R.O.C.) \\
chiaheng@gmail.com}
}

\maketitle

\begin{abstract} 
%cite IoT data subscription economy
The Internet of Things (IoT) makes our lives simpler and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources. The real-time data exchange among devices are periodical that only data in a specific time period is interested. Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case. Additionally, the economic layer built on top of subscription-based pricing models as Software-as-a-Service (SaaS) enables monetizing the subscription relationship, which the payment of data streams is calculated with data usage instead of a particular price for a fixed data set. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification. Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threatens the trust foundation of the entire system. Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required. In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.
\end{abstract}

\begin{IEEEkeywords}
publish/subscribe, data trading, decentralization, Distributed Ledger Technology
\end{IEEEkeywords}

\section{Introduction}
In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing mechanism where data providers and data consumers meet.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{system_design}
    \caption{The system design of a decentralized data trading infrastructure which consists of data providers, consumers and brokers.}
    \label{fig:system_design}
\end{figure}

%TODO: cite IOTAIndustryMarketplace
\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{The Publish/subscribe Communication Models Over Blockchain}
The pub/sub service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in pub/sub system built on top of blockchain focused on the reliability, scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.

@@

\section{System Design Thinking}
\label{section:design_thinking}
\subsection{Data subscription-based trading platform players}
There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. As shown in Fig.~\ref{fig:pub_sub_model}.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{pub_sub_model}
    \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
    \label{fig:pub_sub_model}
\end{figure}

@@

\begin{figure*}[!t]
    \centering
    \includegraphics[width=\linewidth]{channel_and_key}
    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures. Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
    \label{fig:channel_and_key}
\end{figure*}

@@

@@

\begin{table}[h]
	\caption{The comparison of centralized and decentralized identity model}
	\label{tab:did}
	\begin{tabularx}{\linewidth}{|l|X|X|}
	\hline
		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
		\hline
		Control & Enterprises control identities & Entities control their identities \\
		\hline
		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
		\hline
		Portability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
		\hline
	\end{tabularx}
\end{table}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.in]{DID_VC}
    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
    \label{fig:did_vc}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{TangleID}
    \caption{To participate the data trading, players are required to have DID document issued by TangleID. The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication. When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange. The data provider can then retrieve the consumer's public key and encrypt the content with it. After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
    \label{fig:TangleID}
\end{figure}

\subsection{Enable Automated Trading Process}
\begin{figure*}[t]
    \centering
    \includegraphics[width=4in]{smart_contract_mam}
    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts. Participants can easily retrieve information via Product Contract and proceed trading. For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color. The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
    \label{fig:smart_contract_mam}
\end{figure*}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

@@

\section{Masked Authenticated Messaging}
\label{section:MAM}
MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle. The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only. With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{mam_structure}
    \caption{With a seed, users can generate multiple channels, which can then generate multiple endpoints. The IDs of channel and endpoint are the roots of different Merkle trees in MSS. The "central endpoint" are endpoints that has ID, where $endpoint\ ID = channel\ ID$.}
    \label{fig:mam_structure}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{ta_structure}
    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration. It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed. Tangle-accelerators also form a firewall for full nodes, which don't need to reveal the IP address to public and reduce the risks of being attacks.}
    \label{fig:ta_struct}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{delegation}
    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Tangle-accelerator.}
    \label{fig:delegation}
\end{figure}

@@

%pic
\begin{figure*}[!t]
    \centering
    \includegraphics[width=\linewidth]{MAM_E2EE}
    \caption{The process of E2EE.}
    \label{fig:MAM_E2EE}
\end{figure*}

@@

\section{Decentralized Subscription-based Data Trading Case Study}
\label{section:trading_model}
In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{launching_product}
    \caption{The process of launching a product.}
    \label{fig:launching_product}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{key_exchange}
    \caption{Encryption key exchange process.}
    \label{fig:key_exchange}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{unsubscribe}
    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively. Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
    \label{fig:unsubscribe}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.5in]{refund}
    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers. Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
    \label{fig:refund}
\end{figure}

\section{Evaluations}
\label{section:evaluation}
It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle. Each role is only required to run client libraries and communicate with IOTA full nodes to interact with the Tangle. Therefore, in the following evaluations, all devices run with client library only.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{mam_create}
    \caption{Time cost of MAM creation.}
    \label{fig:mam_create}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{mam_send}
    \caption{The probability distributed function of time cost for sending a message through MAM.}
    \label{fig:mam_send}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{rpi3_pow}
    \caption{Local PoW vs. Remote PoW}
    \label{fig:rpi3_pow}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3in]{mam_vs_e2ee}
    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
    \label{fig:mam_vs_e2ee}
\end{figure}

@@

\section{Conclusions}
\label{section:conclusion}
By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.

In the subscription-based data trading, there are some issues that worth discussing and improving. Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation. Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers. Second, brokers are the key to operating a stable system, since they are irreplaceable either from the view of architecture design or trading procedures. However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.

Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service. The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers. Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.

\bibliographystyle{IEEEtran}
\bibliography{references}

>>>>

% ------------------------------------------------
% 常見論文內容次序:
% 1.口試合格證明(初稿不需要)
% 2.中英文摘要(論文以中文撰寫者須附英文延伸摘要)
% 3.誌謝(初稿不需要)
% 4.目錄
% 5.表目錄
% 6.圖目錄
% 7.符號
% 8.主文
% 9.參考文獻
% 10.附錄
%
% 註: 參考文獻書寫注意事項:
% (1).
%    文學院之中文文獻依分類及年代順序排列。
%    其他學院所之文獻依英文姓氏第一個字母
%    (或中文姓氏第一個字筆劃)及年代順序排列。
% (2).
%    期刊文獻之書寫依序為:
%        姓名、文章名稱、期刊名、卷別、期別、頁別、年代。
% (3).
%    書寫之文獻依序為:
%        姓名、書名、出版商名、出版地、頁別、年代。
% ------------------------------------------------

% ------------------------------------------------
%          載入基本設定 Basic configuration
% ------------------------------------------------
% Don't need to modify this section.
\input{configure/configure}

% ------------------------------------------------
%                   DOI Watermark
% ------------------------------------------------
\usepackage{draftwatermark}  % For DOI watermark
\usepackage{listings, makecell, multirow}

\newcommand{\ShowDOI}[1]{
	\SetWatermarkText{\textbf{#1}}
	\SetWatermarkColor{black}
	\SetWatermarkFontSize{0.5 cm}
	\SetWatermarkScale{0.58}
	\SetWatermarkAngle{0}
	\SetWatermarkLightness{0}
	\SetWatermarkHorCenter{18 cm}
	\SetWatermarkVerCenter{28.4 cm}
}

\begin{document}
\ShowDOI{doi:XXXX/NCKU2019XXXXX}

% ------------------------------------------------
%                封面內頁 Inner Cover
% ------------------------------------------------
\singlespacing 
\newpage
\phantomsection
\thispagestyle{empty}
\newgeometry{top=2.3cm,bottom=3cm,left=2cm,right=2cm,nohead,nofoot}

\begin{center}

\begin{minipage}[c][5cm][t]{\textwidth}
  \begin{center}
    \makebox[10cm][s]{\Huge 國立成功大學}\vspace{1cm}		\\
    \makebox[8cm][s]{\Huge 資訊工程研究所}\vspace{1cm}		\\
    \makebox[5cm][s]{\Huge 碩士論文}\vspace{1cm}			\\
    \makebox[5cm][c]{\Huge (初稿)}
  \end{center}
\end{minipage}

\vspace{5.5cm}

\begin{minipage}[c][5cm][t]{\textwidth}
  \begin{center}
    \makebox[\textwidth][c]{\parbox{\paperwidth}
    {\center \Large 針對物聯網資料交易的 \\ 去中心化基礎建設}}
    \vspace{0.5cm}\\
    \makebox[\textwidth][c]{\parbox{\paperwidth}
    {\center \Large A Fully Decentralized Infrastructure for \\ Subscription-based IoT Data Trading}}
  \end{center}
\end{minipage}

\vspace{1.0cm}

\begin{minipage}[c][4.5cm][t]{\textwidth}
  \begin{center}
    {
      % -------------Student-------------
      \hspace{2.0em}
      \makebox[4.0em][r]{\Large 學生：}
      \makebox[6.0em][l]{\Large 林京樺}
      \makebox[8.0em][c]{}
      \makebox[4.0em][r]{\Large Student：}
      \makebox[8.0em][l]{\Large Ching-Hua Lin}
      \vspace{0.5cm}\\
      % -------------Advisor-------------
      \hspace{2.0em}
      \makebox[4.0em][r]{\Large 指導老師：}
      \makebox[6.0em][l]{\Large 涂嘉恒 博士}
      \makebox[8.0em][c]{}
      \makebox[4.0em][r]{\Large Advisor：}
      \makebox[8.0em][l]{\Large Dr. Chia-Heng Tu}
      \vspace{0.1cm}\\
      % -------------Co-Advisor-1-------------
      \hspace{2.0em}
      \makebox[4.0em][r]{\Large 共同指導：}
      \makebox[6.0em][l]{\Large 黃敬群}
      \makebox[8.0em][c]{}
      \makebox[4.0em][r]{\Large Co-Advisor：}
      \makebox[8.0em][l]{\Large Ching-Chun Huang}
      \vspace{0.1cm}\\
    }
  \end{center}
\end{minipage}

\vspace{0.5cm}

\makebox[8cm][s]{\Large 中華民國109年7月}

\end{center}
\restoregeometry
\clearpage
\setstretch{1.2}

% ------------------------------------------------
%  學位考試論文證明書 Defense Certificate (初稿不需要)
% ------------------------------------------------
%\newpage
%\phantomsection
%\thispagestyle{empty}
%\includepdf[pages=-]{context/oral/oral_example.pdf}
%\clearpage

% ------------------------------------------------
%                  摘要 Abstract
% ------------------------------------------------
% 除了外籍生, 本地生和僑生都要同時編寫中文和英文摘要
% 論文以中文撰寫須以英文補寫 800 至 1200 字數的英文延伸摘要 (Extended Abstract)
% 詳細可看附件的學校要求或看example中的英文延伸摘要

% -------------中文摘要-------------
\setcounter{page}{1}
\pagenumbering{roman}
\newpage
\phantomsection
\chapter*{摘要}
\pagestyle{plain}

\begin{spacing}{2.0}

除了外籍生, 本地生和僑生都是要編寫中文和英文摘要. 論文以中文撰寫須以英文補寫 800 至 1200 字數的英文延伸摘要 (Extended Abstract), 如需要的話請修改`./context/abstract/extended.tex'.

外籍生則可免填中文摘要, 而在上傳時網頁資訊需填上`NONE'.

\end{spacing}

\par{\noindent \bf 關鍵字:}{關鍵字1, 關鍵字2, 關鍵字3, 關鍵字4}
\clearpage
\setstretch{1.2}

% -------------English Abstract-------------
\newpage
\phantomsection
\chapter*{Abstract}
\pagestyle{plain}

\begin{spacing}{2.0}

The Internet of Things (IoT) makes our lives simpler and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources. The real-time data exchange among devices are periodical that only data in a specific time period is interested. Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case. Additionally, the economic layer built on top of subscription-based pricing models as Software-as-a-Service (SaaS) enables monetizing the subscription relationship, which the payment of data streams is calculated with data usage instead of a particular price for a fixed data set. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification. Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threatens the trust foundation of the entire system. Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required. In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts.

\end{spacing}

\par{\noindent \bf Keyword:}{ publish/subscribe, data trading, decentralization, Distributed Ledger Technology }
\clearpage
\setstretch{1.2}

% ------------------------------------------------
%           誌謝 Acknowledgments(初稿不需要)
% ------------------------------------------------
%\newpage
%\phantomsection
%\chapter*{誌謝}
%\pagestyle{plain}

%\begin{spacing}{2.0}

%在這邊寫你的感謝 (對父母, 老師, 同學, 朋友等的感謝).

%\end{spacing}

%\clearpage
%\setstretch{1.2}

% ------------------------------------------------
%              目錄 Index of contents
% ------------------------------------------------
% 目錄有三種，分為內容、表格及圖片索引

% -------------內容索引-------------
\renewcommand*\contentsname{Table of Contents}
\singlespacing
\newpage
\phantomsection
\pagestyle{plain}
\tableofcontents
\clearpage
\setstretch{1.2}

% -------------表格索引-------------
\listoftables
% -------------圖片索引-------------
\listoffigures

% ------------------------------------------------
%                   Introduction
% ------------------------------------------------
\setcounter{page}{1}
\pagenumbering{arabic}
\newpage
\phantomsection
\chapter{Introduction}
\pagestyle{plain}

\begin{spacing}{2.0}

In IoT, the development of M2M technology\cite{M2M}, cyber physical system (CPS)\cite{CPS}, and Industry 4.0 grow rapidly. As the physical and digital data are deeply intertwined, the interactions among digital twins act as data exchanges\cite{digitaltwin} which brings potential value to IoT applications, such as health care\cite{healthCare}, factories, and vehicles\cite{AutonomousDriving}, and brings up new business models where data is considered as tradeable digital assets. With the diverse data streams generated by different entities and carried across organizations among expanding amount of interconnected devices, it is a challenge for data holders to share and track their data assets. Therefore, data trading platform is viewed as a solution to build a secure, reliable and scalable data sharing mechanism where data providers and data consumers meet.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{img/system_design}
    \caption{The system design of a decentralized data trading infrastructure which consists of data providers, consumers and brokers.}
    \label{fig:system_design}
\end{figure}

\end{spacing}

\clearpage
\setstretch{1.2}

% ------------------------------------------------
%                  Related Work
% ------------------------------------------------
\newpage
\phantomsection
\chapter{Related Work}
\label{section:relatedWork}
\pagestyle{plain}

\begin{spacing}{2.0}

\subsection{The Publish/subscribe Communication Models Over Blockchain}
The pub/sub service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in pub/sub system built on top of blockchain focused on the reliability, scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset.

@@

\end{spacing}

\clearpage
\setstretch{1.2}

% ------------------------------------------------
%               System Design Thinking
% ------------------------------------------------
\newpage
\phantomsection
\chapter{System Design Thinking}
\pagestyle{plain}

\begin{spacing}{2.0}
\label{section:design_thinking}
\subsection{Data subscription-based trading platform players}
There are three major roles, data providers, data consumers and brokers which are similar to the pub/sub messaging model. But unlike the standard pub/sub model where brokers link the publishers and subscribers who are not aware of each others, in our proposed architecture, the brokers are only responsible for message delivery and essential verification processes. As shown in Fig.~\ref{fig:pub_sub_model}.

\begin{figure}
    \centering
    \includegraphics[width=15cm]{img/pub_sub_model}
    \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
    \label{fig:pub_sub_model}
\end{figure}

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=15cm]{img/channel_and_key}
    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures. Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
    \label{fig:channel_and_key}
\end{figure}
\clearpage

@@

\begin{table}[h]
	\caption{The comparison of centralized and decentralized identity model}
	\label{tab:did}
	\begin{tabular}{|c|c|c|}
	\hline
		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
		\hline
		Control & Enterprises control identities & Entities control their identities \\
		\hline
		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
		\hline
		Portability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.in]{img/DID_VC}
    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
    \label{fig:did_vc}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{img/TangleID}
    \caption{To participate the data trading, players are required to have DID document issued by TangleID. The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication. When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange. The data provider can then retrieve the consumer's public key and encrypt the content with it. After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
    \label{fig:TangleID}
\end{figure}

\subsection{Enable Automated Trading Process}
\begin{figure*}[t]
    \centering
    \includegraphics[width=4in]{img/smart_contract_mam}
    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts. Participants can easily retrieve information via Product Contract and proceed trading. For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color. The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
    \label{fig:smart_contract_mam}
\end{figure*}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{img/key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

@@

\end{spacing}
\clearpage
\setstretch{1.2}

% ------------------------------------------------
%                 Masked Authenticated Messaging
% ------------------------------------------------
\newpage
\phantomsection
\chapter{Masked Authenticated Messaging}
\pagestyle{plain}

\begin{spacing}{2.0}
\label{section:MAM}
MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle. The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only. With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{img/mam_structure}
    \caption{With a seed, users can generate multiple channels, which can then generate multiple endpoints. The IDs of channel and endpoint are the roots of different Merkle trees in MSS. The "central endpoint" are endpoints that has ID, where $endpoint\ ID = channel\ ID$.}
    \label{fig:mam_structure}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{img/ta_structure}
    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration. It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed. Tangle-accelerators also form a firewall for full nodes, which don't need to reveal the IP address to public and reduce the risks of being attacks.}
    \label{fig:ta_struct}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{img/delegation}
    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Tangle-accelerator.}
    \label{fig:delegation}
\end{figure}

@@

%pic
\begin{figure*}[!t]
    \centering
    \includegraphics[width=\linewidth]{img/MAM_E2EE}
    \caption{The process of E2EE.}
    \label{fig:MAM_E2EE}
\end{figure*}

@@

\end{spacing}
\clearpage
\setstretch{1.2}

% ------------------------------------------------
%  Decentralized Subscription-based Data Trading Case Study
% ------------------------------------------------
\newpage
\phantomsection
\chapter{Decentralized Subscription-based Data Trading Case Study}
\pagestyle{plain}

\begin{spacing}{2.0}
\label{section:trading_model}
In this section, we illustrate how participants can join the data subscription platform, start subscribing, cancel subscription, and request refund.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{img/launching_product}
    \caption{The process of launching a product.}
    \label{fig:launching_product}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{img/key_exchange}
    \caption{Encryption key exchange process.}
    \label{fig:key_exchange}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{img/unsubscribe}
    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively. Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
    \label{fig:unsubscribe}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.5in]{img/refund}
    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers. Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
    \label{fig:refund}
\end{figure}

\end{spacing}

\clearpage
\setstretch{1.2}

% ------------------------------------------------
%                   Evaluation
% ------------------------------------------------
\newpage
\phantomsection
\chapter{Conclusion}
\pagestyle{plain}

\begin{spacing}{2.0}
\label{section:evaluation}
It is worth making a claim that all participants in data marketplace do not need to hold an IOTA full node which maintains the transaction history and exchanges information of the Tangle. Each role is only required to run client libraries and communicate with IOTA full nodes to interact with the Tangle. Therefore, in the following evaluations, all devices run with client library only.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{img/mam_create}
    \caption{Time cost of MAM creation.}
    \label{fig:mam_create}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{img/mam_send}
    \caption{The probability distributed function of time cost for sending a message through MAM.}
    \label{fig:mam_send}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{img/rpi3_pow}
    \caption{Local PoW vs. Remote PoW}
    \label{fig:rpi3_pow}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3in]{img/mam_vs_e2ee}
    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
    \label{fig:mam_vs_e2ee}
\end{figure}

@@

\end{spacing}

\clearpage
\setstretch{1.2}

% ------------------------------------------------
%                   Conclusion
% ------------------------------------------------
\newpage
\phantomsection
\chapter{Conclusion}
\label{section:conclusion}
\pagestyle{plain}

\begin{spacing}{2.0}

By combining the established standards and openly-developed specifications, this paper proposed an autonomous publish/subscribe model design to serve as a vendor and industry-neutral platform, automating the trading of digital assets and services. It was built with blockchain network, immutable audit trails, and contracts with an integrated decentralized identity system, to ensure the authenticity of all participants, enable secure communication and flexible trading mechanisms.

In the subscription-based data trading, there are some issues that worth discussing and improving. Firstly, reduce the Gas usage of trading models, as we mentioned in Section~\ref{section:smart_contract_evaluation}, the key exchange process consumes a lot of Gas due to the frequent store operation. Therefore, it is worth discussing that how zero-knowledge protocol could used to exchange key with lower cost, and even validate the key within transfers. Second, brokers are the key to operate a stable system, since they are irreplaceable either from the view of architecture design or trading procedures. However, the issues such as the minimum number of brokers needed to operation the system, and the evaluation of adopting gossip protocol among brokers to gossipped trading status, which enables other brokers to handle trading process when on crashed.

Third, to let consumers search and find interested data products, a search engine is needed to collect all distributed data products, which might need an authority to design and run the service. The extending issue of searching is ranking, how would the search service provider rank the products, how would that affect data consumers and providers. Fourth, in our design, we do not restrict the qualifications of data providers and brokers, which is different from operating the App store currently ,and it is also an interesting issue to discuss.
\end{spacing}

\clearpage
\setstretch{1.2}

% ------------------------------------------------
%               參考文獻 References
% ------------------------------------------------
% References and bibliography

% Import the files that contain your references.
% If you set some references file,
% you need to use at least one cite to make Latex work.
\singlespacing
\newpage
\phantomsection
\renewcommand\bibname{References}	% references title

% 學校規定以作者英文姓氏第一字排列順序，故使用 plain ，如果要按照引用順序，可改用 ieeetr
\bibliographystyle{plain}			% reference style
\bibliography{thesis}				% target .bib file

\clearpage
\setstretch{1.2}

% ------------------------------------------------
%                   附錄 Appendix
% ------------------------------------------------
\BeginAppendixChapter				% User-defined function
\SetupAppendixNumberingFormat		% User-defined function
\newpage
\phantomsection
\chapter{Title of Appendix A}

\begin{spacing}{2.0}

Write your Appendix here.

  \section{Dolor sit amet}
    Appendix

\end{spacing}

\clearpage
\setstretch{1.2}
